%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                               XRTGRAPH                                %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{XrtGraph}
\label{sec:uixrtgraph}
Plots of type \XRTGRAPH{} can be used to produce 2-dimensional graphs
of datapool values.
\index{Plot!XrtGraph}

\input{diagrams/ui_xrtgraph_list}
\index{XRTGRAPH@\XRTGRAPH}

Pressing the right mouse button within such a diagram pops up a menu which
provides additional configuration functions.

\label{uixrtgraphoptions}
\input{diagrams/ui_xrtgraph_option}

\index{CAPTION@\CAPTION!xrtgraph option}
\index{PRINTSTYLE@\PRINTSTYLE!xrtgraph option}
\index{TRUE@\TRUE!xrtgraph option printstyle}
\index{XRTGRAPH@\XRTGRAPH!CAPTION}
\begin{tabularx}{\textwidth}{l|X}
options          & description \\ 
\hline
string           & Print-menu label \\
\CAPTION         & Titel displayed at the bottom of the graphics-form. \\
                 & Using special-characters such as space, you need to use string-representation. \\
\PRINTSTYLE      & = TRUE use extra resources for printing (fonts, line styles, background etc.). \\
\MINMAX          & show(TRUE, default) or hide (FALSE) min and max of a selected curve. \\
\RMS             & show(TRUE, default) or hide (FALSE) rms of a selected curve. \\
\AVG             & show(TRUE, default) or hide (FALSE) avg and max of a selected curve. \\

\end{tabularx}
\newpage

\input{diagrams/ui_xrtgraph_graph}
\input{diagrams/ui_xrtgraph_graph_option}
\input{diagrams/ui_xrtgraph_graph_axis_item}

\index{XAXIS@\XAXIS!xrtgraph graph option}
\index{YAXIS1@\YAXISONE!xrtgraph graph option}
\index{YAXIS2@\YAXISTWO!xrtgraph graph option}
\index{AXES\_ORIGIN\_X@\AXESORIGINX!xrtgraph graph option}
\index{AXES\_ORIGIN\_Y@\AXESORIGINY!xrtgraph graph option}
\index{LOG\_X@\LOGX!xrtgraph graph option}
\index{LOG\_Y@\LOGY!xrtgraph graph option}
\index{XANNOTATION@\XANNOTATION!xrtgraph graph option}
\begin{tabularx}{\textwidth}{l|X}
graph options      & description \\
\hline
\verb+string+      & defines the xrt graph title that will be printed at the top
                     of the plot.\\
\verb+identifier+  & defines the xrt3d graph title that will be printed at the top
                     of the plot. The identifier must be a previously declared stream.
                     (see section \nameref{sec:streamer} on page \pageref{sec:streamer})\\
\XAXIS             & defines the x-coordinates\\
\YAXISONE          & defines coordinates of first Y-Axis\\
\YAXISTWO          & defines coordinates of second Y-Axis\\
\AXESORIGINX       & defines the origin for the x axis\\
\AXESORIGINY       & defines the origin for all y axes\\
\LOGX              & the x-axis is scaled logarithmically\\
\LOGY              & the y-axis is scaled logarithmically\\
\COMBOBOX          & displays the item names as a combobox when the config menu
                          is opened pressing the right mouse button over the plot. \\
\STYLE             & style of all curves. \\
\YONESTYLE         & style of y1 curves. \\
\YTWOSTYLE         & style of y2 curves. \\
\ALLCYCLES         & Shows data of each cylcle in same graph. \\
\SCROLLBARS        & Shows scroll-bars in 'zoomed zone' mode. \\
\XANNOTATION       & Shows x-axis as defined in x-graph-item option XANNOTATION on page
                        \pageref{uixrtgraphitemoptions}. \\
\end{tabularx}

\input{diagrams/ui_xrtgraph_xaxis_label}
\input{diagrams/ui_xrtgraph_yaxis1_label}

\begin{tabularx}{\textwidth}{l|X}
axis-options & description \\
\hline
\LABEL       & Text to display for describing the axis. \\
\end{tabularx}

\input{diagrams/ui_xrtgraph_style}

\begin{tabularx}{\textwidth}{l|X}
plot styles        & description \\
\hline
\BAR               & see hardcopy example on page \pageref{hc:plot2d_style_bar} \\
\AREA              & see hardcopy example on page \pageref{hc:plot2d_style_area} \\
\PLOT              & see hardcopy example on page \pageref{hc:plot2d_style_plot} \\
\POLAR             & see hardcopy example on page \pageref{hc:plot2d_style_polar} \\
\STACKINGBAR       & see hardcopy example on page \pageref{hc:plot2d_style_stacking_bar} \\
\STEP              & see hardcopy example on page \pageref{hc:plot2d_style_step} \\
\end{tabularx}

\input{diagrams/ui_xrtgraph_item}

\index{scale}
\begin{tabularx}{\textwidth}{l|X}
2d item list & description \\
\hline
\verb+scale+ & see section \nameref{sec:scale} page \pageref{sec:scale}. \\
\end{tabularx}

\input{diagrams/ui_xrtgraph_item_option}
\label{uixrtgraphitemoptions}
\index{LABEL@\LABEL!xrtgraph item option}
\index{UNIT@\UNIT!xrtgraph item option}
\index{YAXIS1@\YAXISONE!xrtgraph item option}
\index{YAXIS2@\YAXISTWO!xrtgraph item option}
\index{XAXIS@\XAXIS!xrtgraph item option}
\index{HIDDEN@\HIDDEN!xrtgraph item option}
\index{XANNOTATION@\XANNOTATION!xrtgraph item option}
\index{LINESTYLE@\LINESTYLE!xrtgraph item option}
\index{LINEAR@\LINEAR!xrtgraph item option}
\index{STEP@\STEP!xrtgraph item option}


\begin{tabularx}{\textwidth}{l|X}
graph item options & description \\ 
\hline
\LABEL        & defines the item name which will be printed at the top of the axis\\
\UNIT         & defines the unit description which will be printed at the top of the axis\\
\YAXISONE     & defines the y-coordinates of the left y axis\\
\YAXISTWO     & defines the y-coordinates of the right y axis\\
\XAXIS        & defines the coordinates of the x axis\\
\HIDDEN       & does not print any description at the top of the axis\\
\XANNOTATION  & defines extra labels for x axis\\
\LINESTYLE    & defines the line style \\
\LINEAR       & TODO \\
\STEP         & TODO \\
\end{tabularx}

\input{diagrams/ui_xrtgraph_item_anno}
\input{diagrams/ui_xrtgraph_item_anno_title}
\input{diagrams/ui_xrtgraph_item_anno_values}
\input{diagrams/ui_xrtgraph_item_anno_labels}
\input{diagrams/ui_xrtgraph_item_anno_angle}
\label{uixrtgraphitemoptionsxannotation}

\index{LABEL@\LABEL!xrtgraph option!xannotation}
\index{XANNOTATION@\XANNOTATION!xrtgraph x graph option}
\index{Scale factors!xrtgraph xannotation}
\begin{tabularx}{\textwidth}{l|X}
graph item options & description \\ 
\hline
\LABEL             & title which will be printed at the bottom of graphics \\
\verb+anno values+ & {\bfseries data item}: position on the x axis, where labels will be displayed.\\
\verb+scale+       & scale factor (see section \nameref{sec:scale} page \pageref{sec:scale}). \\
\verb+anno labels+ & {\bfseries string data item}: labels to be displayed at display position.\\
\verb+anno angle+  & angle (in degrees) to print the labels. Default is 90 (vertical). 0 is horizontal. \\
\end{tabularx}


\begin{boxedminipage}[t]{\linewidth}
\begin{alltt}
\DESCRIPTION "Example XRTGRAPH";
\DATAPOOL
  \REAL \{\EDITABLE\}
    xValues
   ,y1Values
   ,y2Values
   ;
\END \DATAPOOL;

\UIMANAGER
  \XRTGRAPH
    graph_plot
      \{ \CAPTION = streamCaption \}
      ( plot
           \{ streamTitel
           , \XAXIS = xValues \{ \LABEL = "X-Axis" \}
           \}
         (
           xValues,
           y1Values \{\YAXISONE\},
           y2Values \{\YAXISTWO\}
         )
      );
  \FORM
    Form_XrtGraph \{"Graph Plot", \HIDECYCLE\}
      ( ( graph_plot )
      );
\END \UIMANAGER;
\END.
\end{alltt}
\end{boxedminipage}

