\newpage
\subsubsection{String}
%              ------
\label{sec:string}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                               String                                  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\index{String!concatenation}
Strings are used in almost every section of this manual.
They must be delimited by a double quote character (''): \\

\input{diagrams/string}
\input{diagrams/string_element}
\input{diagrams/STRING_CONSTANT}

\index{  @Signs / Characters!\texttt{""} (double quote)!string delimiter}
\index{  @Signs / Characters!\& (ampersand)!string concatenation}
\index{COMPOSESTRING@\COMPOSESTRING!string composition}
\index{RESOURCE@\RESOURCE!resource string value}
\index{LABEL@\LABEL!string concatenation}
\index{UNIT@\UNIT!string concatenation}
\begin{tabularx}{\textwidth}{l|X}
string    & Description \\
\hline
character & any charachter sign, except double quote (''), at (@) and backslash ($\backslash$) \\
  & double quotes are used to delimit the string \\
  & at's are used to switch between fonts (see section multifont
             strings \nameref{sec:multifont} page \pageref{sec:multifont})\\
\&  & concatenate string with strings, LABEL's or UNIT's \\
\verb+_("...")+ & a string that can be translated (using GNU gettext) \\
\RESOURCE      & see section \nameref{sec:resource} on page \pageref{sec:resource} \\
\COMPOSESTRING & Compose string: write values into string. Needed for translatable strings or to use a \RESOURCE{} value in a string. \newline
                 The format-string (first argument) contains \%1, \%2, ... and the remaining value(s)
                 (integer or string) are put in these places. \newline
                 One format-string with up to 3 integers or 15 strings are implemented. \newline
                 The composition is done at parse time. \\
LABEL & returns the label defined in the datapool (section
               \nameref{dia:dataitemoptions} page \pageref{dia:dataitemoptions}). \\
UNIT  & returns the unit description defined in datapool (section
              \nameref{dia:dataitemoptions} page \pageref{dia:dataitemoptions}). \\
\verb+ID_DATAVARIABLE+ & references a data item declared in datapool (section
              \nameref{sec:dpitem} page \pageref{sec:dpitem}). For options like
              \LABEL{} and \UNIT{} use data items without indexes. \\
\verb+ID_DATASET+ & references a data set declared in datapool (section
              \nameref{sec:dpset} page \pageref{sec:dpset}). \\
\verb+.+          & structure item separator \\
                  & Structures are explained in section \nameref{sec:dpstruct}
                  page \pageref{sec:dpstruct}\\
\verb+identifier+ & references a data item declared in datapool (section
              \nameref{sec:dpitem} page \pageref{sec:dpitem}). \\
\end{tabularx}

%%\subsubsection{Examples}
\label{sec:identifierexamples}

Example:

\begin{boxedminipage}[t]{\linewidth}
\begin{verbatim}
"This is a string delimited by double quotes"
"This is a " & "String"

"This string is concatenated with " & LABEL(data_item_identifier)
\end{verbatim}
\end{boxedminipage}
\vspace{1cm}

\begin{multicols}{2}
\input{diagrams/filename_string}
\input{diagrams/title_string}
\input{diagrams/bg_color_string}
\input{diagrams/document_string}
\input{diagrams/label_string}
\input{diagrams/fg_color_string}
\end{multicols}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                               Character                               %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{diagrams/char_const}

A CHAR\_CONSTANT is a single character.
It must be delimited by a single quote sign (').
